---
title: "SEC 2-FA2 GROUP4-EDUVALA, MIKHAEL"                    
subtitle: "GITHUB - Probability and Probability Distribution" 
output: pdf_document                                          
date: "2026-08-30"                                            
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 3. An experiment consists of rolling a die. Use R to simulate this experiment 600 times and obtain the relative frequency of each possible outcome. Hence, estimate the probability of getting each of 1, 2, 3, 4, 5, and 6.

```{r}
x <- c(1,2,3,4,5,6)

experiment <- sample(x, 600, replace = TRUE)

frequency <- table(experiment)
print(frequency)

bar <- barplot(frequency, names.arg = x, main = "Frequency of a Die rolling for 600 times",
               xlab = "Outcomes", ylab = "Frequency", ylim = c(0,max(frequency)),col="#FFC300")

text(bar, frequency, labels = frequency, cex = 1, pos = 1)

```

##Shown above is the frequency of a die getting 1,2,3,4,5,6 for 600 times

## Relative Frequency:

Here is the estimated probability of getting each 1,2,3,4,5,6 in a die.

```{r}
relative_frequency <- frequency / 600
print(relative_frequency)

pie(
  relative_frequency,
  labels = paste0(
    names(relative_frequency),
    " (", round(relative_frequency * 100, 1), "%)"
  ),
  main = "Relative Frequency of Die Rolls"
)


```

##The Pie Chart above shows the relative frequency of getting 1,2,3,4,5,6 in a die rolling for 600 times
