---
title: "SEC 2-FA3 GROUP4-EDUVALA, MIKHAEL"                    
subtitle: "GITHUB - "
output: pdf_document                                          
date: "2026-09-06"    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## A geospatial analysis system has four sensors supplying images. The percentage of images supplied by each sensor and the percentage of images relevant to a query are shown in the following table.

```{r}
images <- data.frame(sensor = 1:4, Supplied = c(0.15, 0.20, 0.25, 0.40), Relevant = c(0.50, 0.60, 0.80, 0.85))
```

## What is the overall percentage of relevant images?

R = Relevant, S = Supplied

$$ P(R) = P(R \vert S_1) \cdot P(S_1) + P(R \vert S_2) \cdot P(S_2) + P(R \vert S_3) \cdot P(S_3) + P(R\vert S_4)\cdot P(S_4) $$

```{r}
prob_rel <- sum(images$Supplied * images$Relevant)
cat("The overall percentage of relevant images is ", prob_rel * 100, "%.", sep = "")
```

## 6.A fair coin is tossed twice. Let $E_1$ be the event that both tosses have the same outcome, that is $E_1 = (HH, TT)$. Let $E_2$ be the event that the first toss is a head, that is, $E_2 = (HH, HT)$. Let $E_3$ be the event that the second toss is a head, that it, $E_3 = (TH, HH)$. Show that $E_1, E_2, \text{and } E_3$ are pairwise independent but not mutually independent.

## Sample Spaces

$$S = {HH, HT, TH, TT}$$

each outcome has an equal probability: $$P({HH}) = P({HT}) = P({TH}) = P({TT}) = \frac{1}{4}$$

## Events and Their Probabilities

1.  $E_1 = (HH, TT)$
    - $P(E_1) = P(HH) + P(TT) = \frac{1}{4} + \frac{1}{4} = \frac{1}{2}$
2.  $E_2 = (HH, HT)$
    - $P(E_2) = P(HH) + P(HT) = \frac{1}{4} + \frac{1}{4} = \frac{1}{2}$
3.  $E_3 = (TH, HH)$
    - $P(E_3) = P(TH) + P(HH) = \frac{1}{4} + \frac{1}{4} = \frac{1}{2}$

### There are 4 possible outcomes when a coin is tossed twice.

```{r}
sample <- c("HH","TT", "HT", "TH")

E1 <- c("HH", "TT")
E2 <- c("HH", "HT")
E3 <- c("TH",  "HH")

PE1 <- length(E1) / length(sample)
PE2 <- length(E2) / length(sample)
PE3 <- length(E3) / length(sample)

PE1
PE2
PE3
```

## FIND THE INTERSECTION

### Check if E1 and E2 are independent

```{r}
#### OUTCOMES THAT ARE IN BOTH E1 AND E2

E1E2 <- intersect(E1, E2)

#### PROBABILITY 

PE1E2 <- length(E1E2) / length(sample)

PE1xE2 <- PE1 * PE2

E1E2

PE1E2

PE1xE2
```

## Check if E1 and E3 are independent

```{r}
#### OUTCOMES THAT ARE IN BOTH E1 AND E3

E1E3 <- intersect(E1, E3)

#### PROBABILITY 

PE1E3 <- length(E1E2) / length(sample)

PE1xE3 <- PE1 * PE2

E1E3

PE1E3

PE1xE3
```

## Check if E2 and E3 are independent

```{r}
#### OUTCOMES THAT ARE IN BOTH E2 AND E3

E2E3 <- intersect(E2, E3)

#### PROBABILITY 

PE2E3 <- length(E1E2) / length(sample)

PE2xE3 <- PE1 * PE2

E2E3

PE2E3

PE2xE3
```

## OR

if $$P(A \cap B) = P(A) P(B)$$, then vents $A$ and $B$ are independent

1.  $E_1 \text{ and } E_2 \newline E_1 \cap E_2 = \{HH\} \newline  P(E_1 \cap E_2) = P(HH) = \frac{1}{4} \newline P(E_1) P(E_2) = \frac{1}{2} \times \frac{1}{2} = \frac{1}{4}\newline$ Since $P(E_1 \cap E_2) =  P(E_1) P(E_2)$, $E_1 \text{ and } E_2$ are independent.

2.  $E_1 \text{ and } E_3 \newline E_1 \cap E_3 = \{HH\} \newline  P(E_1 \cap E_3) = P(HH) = \frac{1}{4} \newline P(E_1) P(E_3) = \frac{1}{2} \times \frac{1}{2} = \frac{1}{4}\newline$ Since $P(E_1 \cap E_3) =  P(E_1) P(E_3)$, $E_1 \text{ and } E_3$ are independent.

3.  $E_2 \text{ and } E_3 \newline E_2 \cap E_3 = \{HH\} \newline  P(E_2 \cap E_3) = P(HH) = \frac{1}{4} \newline P(E_2) P(E_3) = \frac{1}{2} \times \frac{1}{2} = \frac{1}{4}\newline$ Since $P(E_2 \cap E_3) =  P(E_2) P(E_3)$, $E_2 \text{ and } E_3$ are independent.

## Mutual Independence

```{r}
all <- intersect(intersect(E1, E2), E3)
p_all <- length(all) / length(sample)
p_product <- PE1 * PE2 * PE3

all
p_all
p_product

```

#### The Events Are Not Mutually Independent

$E_1, E_2, \dotsc , E_k$ are mutually independent if: $$P(E_{i_1} \cap E_{i_2} \cap \dotsm \cap E_{i_k}) = P(E_{i_1})P(E_{i_2})\dotsm P(E_{i_k})$$

From the sets: $\newline E_1 \cap E_2 \cap E_3 = \{HH\} \newline P(E_1 \cap E_2 \cap E_3) = P(HH) = \frac{1}{4}$

Calculate $P(E_1)P(E_2)P(E_3)$: $\newline P(E_1)P(E_2)P(E_3) = \frac{1}{2} \times \frac{1}{2} \times \frac{1}{2} = \frac{1}{8}\newline$

Since $P(E_1 \cap E_2 \cap E_3) \neq P(E_1)P(E_2)P(E_3)$, then the events are not mutually independent.
